Delta Factor - A New Authorization Factor

### 2022-08-07 paper1.tex
---

%------------------------------------------------------------------------------%---------------------------------------
%------------------------------------------------------------------------------%---------------------------------------

\section{CITATIONS - Chicago style} % OUT-OF-ORDER intentional. Point number before "CITATIONS" auto-changed 
\noindent
Public Internet Standards (Various Authors)

@@

\noindent
Reference implementations provided by papers + standardized code\\
TOTP - https://datatracker.ietf.org/doc/html/rfc6238\\
HOTP - https://datatracker.ietf.org/doc/html/rfc4226 \\
COTP - (\textbf{citation TBA})\\

\noindent
Collecting TCP Timings via Performance API\\
https://developer.mozilla.org/en-US/docs/Web/API/Performance\\
Collecting TLS Information via Security Info from Extensions JS API\\
https://developer.mozilla.org/en-US/docs/Mozilla/Add-ons/WebExtensions/API/webRequest/SecurityInfo\\

@@

%---------------------------------------------------------------------------------------------------------------------

>>>>

%------------------------------------------------------------------------------%---------------------------------------
%------------------------------------------------------------------------------%---------------------------------------
\section{CITATIONS \normalfont{Chicago style:}} 	% Same as "References" as per prof
\noindent
Public Internet Standards (Various Authors)

@@

\noindent
Reference implementations provided by papers + standardized code\\
TOTP - https://datatracker.ietf.org/doc/html/rfc6238\\
HOTP - https://datatracker.ietf.org/doc/html/rfc4226 \\
COTP - (\textbf{citation TBA})\\
COTP implementation - https://github.com/TomEphraimPerez/CS5540-final/tree/webserver /nginx\\

\noindent
Collecting TCP Timings via Performance API\\
https://developer.mozilla.org/en-US/docs/Web/API/Performance\\
Collecting TLS Information via Security Info from Extensions JS API\\
https://developer.mozilla.org/en-US/docs/Mozilla/Add-ons/WebExtensions/API/webRequest /SecurityInfo\\

@@

%---------------------------------------------------------------------------------------------------------------------
\section{Conclusion}
conclusions\\
more\\
